FictionEro2 - Affective Impact of Fiction

### 2025-06-20 study2/analysis/2_emotion.qmd
push

```{r data preparation}
#| warning: false
#| 
dfsub <- read.csv("../data/data_participants.csv")

@@

stars1a <- data.frame(label=c("**","***", "**", "***", "***"),
                    Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Female"), "Male"),
                    Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence"),
                    Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
                    x=c(1.5, 1.5, 1.5, 1.5, 1.5), 
                    y = c(0.53, 0.40, 0.6, 0.51, 0.6))

@@

p1 <- pred1 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
  ggplot(aes(x=StimuliType, y=estimate)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2, key_glyph = "path") +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
  geom_text(data=stars1a, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
  #           aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.6), color="#8BC34A", alpha=0) +
  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
  #           aes(xmin=0.8, xmax=1.2, ymin=0.3, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(Outcome~Gender, switch="y", scales ="free") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = ) +
  labs(color="Images presented as:")

>>>>

```{r data preparation}
#| warning: false

dfsub <- read.csv("../data/data_participants.csv")

@@

stars1a <- data.frame(label=c("**","***", "**", "***", "***", "***"),
                    Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Male", "Female"), "Male"),
                    Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence", "Valence"),
                    Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
                    x=c(1.5, 1.5, 1.5, 1.5, 1.5, 1.5), 
                    y = c(0.53, 0.40, 0.6, 0.51, 0.62, 0.58))

@@

p1 <- pred1 |>
  mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
  ggplot(aes(x=StimuliType, y=estimate)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.4, key_glyph = "path") +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
  geom_text(data=stars1a, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
  #           aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.6), color="#8BC34A", alpha=0) +
  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
  #           aes(xmin=0.8, xmax=1.2, ymin=0.3, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(Outcome~Gender, switch="y", scales ="free") +
  scale_y_continuous(limits=c(0.20, 0.8), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_bw() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = ) +
  labs(color="Images presented as:")
